### 2020-10-27 doc/manuscript/Dow_manuscript.Rmd
table `sample_size_by_year`
#28

# SUPPLEMENTARY INFO
#SI figure numbers
climwin_rp_DOY25_SCBI = "S1"
climwin_dp_DOY25_SCBI = "S2"
climwin_rp_DOY25_SCBI = "S3"
climwin_dp_DOY25_SCBI = "S4"
#SI figure captions
climwin_rp_DOY25_SCBI_short_caption <- "Figure S1. Full climwin output for DOY 25 for ring porous species at SCBI."
climwin_dp_DOY25_SCBI_short_caption <- "Figure S2. Full climwin output for DOY 25 for diffuse porous species at SCBI."
climwin_rp_DOY25_HARV_short_caption <- "Figure S3. Full climwin output for DOY 25 for ring porous species at Harvard Forest."
climwin_dp_DOY25_HARV_short_caption <- "Figure S4. Full climwin output for DOY 25 for diffuse porous species at Harvard Forest."

@@

Within the plot, metal dendrometer bands were installed on *>#* trees and measured with a digital caliper approximately every 1-2 weeks within the growing season for *9* years (*list ranges, for each site if different*). *(don't bother to mention biannual bands, unless you end up using the data--which you could, for annual growth, if you'd like to increase the sample size. You can put exact numbers of bands per year in an SI file.*)  The number of bands measured at each site fluctuated somewhat as trees were added or dropped (e.g., because of tree mortality) from the census *(Table S1)*. Across years, the number of bands sampled averaged *~150* at SCBI, # at Harvard Forest*, and # at SERC*. Four main species were sampled including two diffuse-porous (Lirodendron tulipfera and Fagus grandafolia) and two ring-porous (Quercus rubra and Quercus alba) species.    *(summary of how bands were distributed across species, focusing on ring/ diffuse porous distinction. details in an SI table)*

@@

(Bands After cleaning: 2011- 105 trees; 2012 - 102 trees; 2013 - 102 trees; 2014 - 149 trees; 2015 - 149 trees; 2016 - 149 trees; 2017 - 148 trees; 2018 - 146 trees; 2019 - 145 trees *--put this in Table S1*).

(Bands used after minimum growth checks: 
1  2011    84
2  2012    84
3  2013   100
4  2014   100
5  2015    96
6  2016    94
7  2017    89
8  2018    88
9  2019    75) this seems like alot are being thrown out - manually check if WAI

@@

>>>>

# SUPPLEMENTARY INFO
#SI table numbers
sample_size_by_year= "S1"

#SI table captions
sample_size_by_year_caption <- "Table S1. Sample size by year"

#SI figure numbers
climwin_rp_DOY25_SCBI = "S1"
climwin_dp_DOY25_SCBI = "S2"
climwin_rp_DOY25_SCBI = "S3"
climwin_dp_DOY25_SCBI = "S4"
#SI figure captions
climwin_rp_DOY25_SCBI_short_caption <- "Figure S1. Full climwin output for DOY 25 for ring porous species at SCBI."
climwin_dp_DOY25_SCBI_short_caption <- "Figure S2. Full climwin output for DOY 25 for diffuse porous species at SCBI."
climwin_rp_DOY25_HARV_short_caption <- "Figure S3. Full climwin output for DOY 25 for ring porous species at Harvard Forest."
climwin_dp_DOY25_HARV_short_caption <- "Figure S4. Full climwin output for DOY 25 for diffuse porous species at Harvard Forest."

@@

Within the plot, metal dendrometer bands were installed on *>#* trees and measured with a digital caliper approximately every 1-2 weeks within the growing season for *9* years (*list ranges, for each site if different*). *(don't bother to mention biannual bands, unless you end up using the data--which you could, for annual growth, if you'd like to increase the sample size. You can put exact numbers of bands per year in an SI file.*)  The number of bands measured at each site fluctuated somewhat as trees were added or dropped (e.g., because of tree mortality) from the census (Table `r sample_size_by_year`). Across years, the number of bands sampled averaged *~150* at SCBI, # at Harvard Forest*, and # at SERC*. Four main species were sampled including two diffuse-porous (Lirodendron tulipfera and Fagus grandafolia) and two ring-porous (Quercus rubra and Quercus alba) species.    *(summary of how bands were distributed across species, focusing on ring/ diffuse porous distinction. details in an SI table)*

@@

@@

`r sample_size_by_year_caption`
